A Systematic Review of the Use of the ESM Methodology in Education

### 2020-08-05 paper_draft.Rmd
new changes
update authors, date

---
title: "A Systematic Review of the Use of the ESM Methodology in Education"
author: "Alex Lishinski"
date: "7/24/2020"
output: pdf_document
---

@@

>>>>

---
title: "A Systematic Review of the Use of the ESM Methodology in Education"
author: "Alex Lishinski, Michael Mann, Omiya Sultana"
date: "8/5/2020"
output: pdf_document
---

@@

This study  is a systematic review of studies in education that used the experience sampling method to collect data.
